Classifier Testing

### 2019-03-29 Code/dallin_annotations/16_classifier_testing.Rmd
Updated the 16_classifier_testing file.

### What scripts need to function for this code to work?
predict_func.R
* Renamed as 11_predict_func.Rmd
* NOT WORKING

TweetComplaintPredictor.r
* Renamed as 12_tweet_complaint_predictor.Rmd
* NOT WORKING

### Which models need to be loaded for this code to work?
prccomp4.dat 
* I think this is the PCR model
* NOT FOUND

model50-tweet_sample_2M_noRT.dat.bin 
* It looks like this is a fasttext model, but I'm not sure if it is the supervised or unsupervised.
* NOT FOUND

xgb.modelPC4.dat
* This must be the xg boost model that brings the sub-models together.
* NOT FOUND

```{r}
library(fastrtext)
library(Matrix)
library(xgboost)
source("11_predict_func.Rmd") # Formerly "R/predict_func.R" in Adriel's original code
source("tweet_complaint_predictor.Rmd") # Formerly "R/TweetComplaintPredictor.r" in Adriel's original code

load("complaint-prediction/models/fullClassifierOne/prcomp4.dat")
fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
load("complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat")
TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)

predict(TweetComplaintPredictor, "")
```

>>>>

### What scripts need to function for this code to work?
##### predict_func.R
* Renamed as 11_predict_func.Rmd in this folder.
* NOT WORKING

##### TweetComplaintPredictor.r
* Renamed as 12_tweet_complaint_predictor.Rmd in this folder.
* NOT WORKING

### Which models need to be loaded for this code to work?
##### prcomp4.dat 
* I think this is the PCR model (pr[inciple]comp[onent].dat?)
* FOUND in Code/complaint-prediction/models/fullClassifierOne/prcomp.dat, as stated in the code.
* I moved the file to the /Temporary folder

##### model50-tweet_sample_2M_noRT.dat.bin 
* It looks like this is a fasttext model, but I'm not sure if it is the supervised or unsupervised.
* NOT FOUND

##### xgb.modelPC4.dat
* This must be the xg boost model that brings the sub-models together.
* FOUND in Code/complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat, as stated in the code.
* Moved to the /Temporary Folder

# Libraries
```{r}
library(fastrtext)
library(Matrix)
library(xgboost)
source("11_predict_func.Rmd") # Formerly "R/predict_func.R" in Adriel's original code
source("tweet_complaint_predictor.Rmd") # Formerly "R/TweetComplaintPredictor.r" in Adriel's original code
```

##### Reminder of the WD
```{r}
getwd()
```

# Load Models
```{r}
load("../../Temporary/prcomp4.dat") # Formerly "complaint-prediction/models/fullClassifierOne/prcomp4.dat" in Adriel's original code
fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
load("../../Temporary/xgb.modelPC4.dat") # Formerly "complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat" in Adriel's original code
TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)

```

# Test Classifier
Using this predict() function, we can make predictions about single tweets. All you have to do is type your tweet in the quotations for the second argument. 
```{r}
predict(TweetComplaintPredictor, "")

```
